Comparing to lognormal, Poisson, exponential

### 2021-03-09 analysis/rev_prototyping/ct_mcdb.Rmd
ct
run gentry and mcdb

@@

>>>>

ggplot(all_di, aes(real_po_percentile_excl)) + geom_histogram()

ggplot(all_di, aes(nparts, sim_pos_from_best)) +
  geom_point() +
  scale_x_log10()

@@

ggplot(all_di, aes(sim_r2_from_best_median)) +
  geom_histogram()

ggplot(all_di, aes(sim_r2_from_best_median, real_r2)) +
  geom_point() +
  geom_line(aes(sim_r2_from_best_median, sim_r2_from_best_median)) +
  ylim(0,1)

ggplot(all_di, aes(real_po_percentile_excl)) + geom_histogram()

ggplot(all_di, aes(nparts, sim_r2_from_best_median)) +
  geom_point() +
  scale_x_log10()
